R Packages to Aid in Handling Web Access Logs

### 2015-12-26 paper/paper.Rmd
formatting

The standard for URLs \citep{RFC1738} divides them into a heirarchical sequence of components - the scheme ("http"), host ("en.wikipedia.org"), port ("800"), path ("wiki/Main_Page") and searchpart, or parameters ("action=edit"). Together, these make
up a URL ("http://en.wikipedia.org:800/wiki/Main_Page?action=edit").

>>>>

The standard for URLs \citep{RFC1738} divides them into a heirarchical sequence of components - the scheme (\samp{http}), host (\samp{en.wikipedia.org}), port (\samp{800}), path (\samp{wiki/Main\_Page}) and searchpart, or parameters (\samp{action=edit}). Together, these make up a URL
\linebreak (\samp{http://en.wikipedia.org:800/wiki/Main\_Page?action=edit}).

### 2015-12-26 paper/paper.tex
formatting

The standard for URLs \citep{RFC1738} divides them into a heirarchical
sequence of components - the scheme (``http''), host
(``en.wikipedia.org''), port (``800''), path (``wiki/Main\_Page'') and
searchpart, or parameters (``action=edit''). Together, these make up a
URL (``\url{http://en.wikipedia.org:800/wiki/Main_Page?action=edit}'').

>>>>

The standard for URLs \citep{RFC1738} divides them into a heirarchical
sequence of components - the scheme (\samp{http}), host
(\samp{en.wikipedia.org}), port (\samp{800}), path
(\samp{wiki/Main\_Page}) and searchpart, or parameters
(\samp{action=edit}). Together, these make up a URL
\linebreak (\samp{http://en.wikipedia.org:800/wiki/Main\_Page?action=edit}).
